---
title: "The Normal Distribution"
output: html_notebook
---

```{r}
dnorm(-3)
```

```{r}
x <- seq(from=-4, to=4, len=100)
plot(x, dnorm(x), main = "PDF of standard normal distribution", ylab = "density")
```

```{r}
x <- seq(from=-4, to=4, by=0.05)
plot(x, dnorm(x), main = "PDF of standard normal distribution", ylab = "density")
```

```{r}
x <- seq(from=-3, to=3, len=100)
plot(x, dnorm(x), type="l", main = "CDF of standard normal distribution", ylab = "density")
x <- x[x<1.3]
polygon(x=c(x, rev(x)), y=dnorm(c(x+1e100, rev(x))), border=NA, col='gray')
```

```{r}
pnorm(1.3)
```

```{r}
table(rnorm(1e6) < 1.3)/1e6

```

N(5, 2.2) \< 6.1

```{r}
pnorm(6.1, 5, 2.2)
```

```{r}
1 - pnorm(4.3, 5, 2.2)
```

11.2 \< x \< 11.9, N(10, 2.2)

```{r}
pnorm(11.9, 10, 2.2) - pnorm(11.2, 10, 2.2)
```

```{r}
x = rnorm(1e6, 10, 2.2)
table(x > 11.2 & x < 11.9)
```

```{r}
qnorm(0.95)
```

```{r}
pnorm(1.644854)
```

```{r}
table(rnorm(1e6) < qnorm(0.95))/1e6
```

```{r}
table(rnorm(1e6) > qnorm(0.05))/1e6
```

```{r}
p <- seq(from=0.01, to=0.99, len=100)
plot(p, qnorm(p), type = 'l')
```

```{r}
plot(0:100, dbinom(0:100, 100, 0.3), type='h')
```

```{r}
mean(rbinom(1e6, 10, 0.3))
sd(rbinom(1e6, 10, 0.3))
```

```{r}
x <- seq(from=-3, to=10, len=100)
plot(x, pnorm(x, 6, sqrt(20*0.3*(1-0.3))), type='l', ylab="cumulative probability")
points(x, pbinom(x, 20, 0.3), type = 'l', col='red')
legend("topleft", lty = 1, col=c('red', 'black'), legend=c('binomial', 'normal'))
```

```{r}
x <- seq(from=-25, to=100, len=200)
plot(x, dnorm(x, 6, sqrt(100*0.3*(1-0.3))), type='l', ylab="PDF")
points(-25:100, dbinom(-25:100, 100, 0.3), type = 'l', col='red')
legend("topleft", lty = 1, col=c('red', 'black'), legend=c('binomial', 'normal'))

```
